On Devon Allen's Disqualification at the 2022 Track and Field World Championship

### 2023-04-18 Manuscript/manuscript.tex
Updates from 4/18 meeting

Once the Gamma mixed effects model was chosen, it needed to be decided which combination
of effects to use.  It was possible to include a venue effect, a batch effect, 
or a year and batch effect.  The batch effect is very
difficult to explain or interpret as it means that some heats of races were either
faster or slower and that everyone in the batch reacted similarly.  Although
it is possible that one athlete reacting faster could lead to others reacting
similarly, this does not make much practical sense as the difference between
heats that had fast and slow reaction times are all within 0.12 seconds of each
other.  It is much easier however to explain the venue effect.  The technology
that World Athletics has used has differed since 1999 and theoretically the
reaction time data from 2022 should be the best as the timing system should be
state of the art.  Any other weather or climate related factors such as humidity,
precipitation, elevation, etc. would all be negated when looking at the batch
effect, but are all factors that could potentially impact the venue effect.
Thus, we decided to inclue only the venue effect in the GLMM, which is presented
as:

\begin{equation}
  \label{eq:GLMM}
  Y_{ij} = \beta_0 + \gamma_i + \epsilon_{ij}
\end{equation}

Where $Y_{ij}$ is the response variable for observation $j$ in year $i$, , 
$\beta_0$ is the intercept, $\gamma_i$ is the random effect term for year $i$, 
and $\epsilon_{ij}$ is the error term for observation $j$ in year $i$.

>>>>

Once the Gamma mixed effects model was chosen, it needed to be decided which combination
of effects to use.  It was possible to include a venue effect, a batch effect, 
or a year and batch effect.  The batch effect is very
difficult to explain or interpret as it means that some heats of races were either
faster or slower and that everyone in the batch reacted similarly.  Although
it is possible that one athlete reacting faster could lead to others reacting
similarly, this does not make much practical sense as the difference between
heats that had fast and slow reaction times are all within 0.12 seconds of each
other.  It is much easier however to explain the venue effect.  The technology
that World Athletics has used has differed since 1999 and theoretically the
reaction time data from 2022 should be the best as the timing system should be
state of the art.  Any other weather or climate related factors such as humidity,
precipitation, elevation, etc. would all be negated when looking at the batch
effect, but are all factors that could potentially impact the venue effect.
Thus, we decided to inclue only the venue effect in the GLMM, which is presented
as:
\begin{equation}
  \label{eq:GLMM}
  Y_{ij} = \beta_0 + \gamma_i + \epsilon_{ij},
\end{equation}
where $Y_{ij}$ is the response variable for observation $j$ in year $i$, 
$\beta_0$ is the intercept, $\gamma_i$ is the random effect term for year $i$, 
and $\epsilon_{ij}$ is the error term for observation $j$ in year $i$.
